%   Filename    : acknowledgment.tex 
\begin{center}
	\textbf{Acknowledgment}
\end{center}

\setlength{\parindent}{0pt}
This special problem would\textsc{\char13}t be possible these trying times. The pandemic really hit all of us hard both mentally anf financially. We all have to adjust in this “new normal”, including school processes like requesting the copy of grades or transcripts. The pandemic really made all of these things very difficult to do and it is also a hassle to everyone involved. For this, we would like to thank all of the students and friends who voiced out their complaints regarding how hassle the process was. 

We would also like to thank the University\textsc{\char13}s Cash Office  and the CAS Office of the College Secretary for helping us understand how the process of requesting documents work nad tips on how to make this process more efficient and more convenient for everyone. 

We would like to thank our consultant and co-adviser for this special problem , Mrs. Christi Florence Cala-or, for always checking in on our progress. 

We would like to thank our friends for always checking in on our progress and slo for pressuring us to to this project.

This special problem is dedicated to everyone who has difficulties in requesting documents in the online setup. This project won\textsc{\char13}t be possible without you. 





\begin{tabular}{lp{4.25in}}
\hspace{-0.5em}\textbf{Keywords:}\hspace{0.25em} & Document request, tracking system, DTS, DRS.\\
\end{tabular}